Stochastic Approximation Monte Carlo with a Dynamic Update Factor

### 2019-08-21 papers/histogram/sad-referee-response.md

We appreciate the referees' careful reading of our paper, and feel that their
feedback has led to a significant improvement.  We have made some significant
edits to the paper in response to their comments.  These edits were focused on
providing a broader background with regard to previous work, increasing clarity,
and general proofreading.  We believe that we have addressed all of the
referees' concerns with the exception of the unreasonable request by the first
referee that we present results on additional new systems.

...

Response to first referee

The first referee acknowledges that our paper is well written and that the field
is an important one, but does not believe that our work is a *'substantial
contribution'* to the field.  The referee has three major criticisms of the
value of our work (aside from issues with the introduction section).

@@

Thirdly, because we find that 1/t-WL converges at the same rate as our method,
the referee concludes that our method is not a substantial improvement. We note
first (as mentioned in the paper in *Section IV*) that the 1/t-WL method is
solving a significantly easier problem, because it is told in advance the range
of energies that are of interest.  We do agree that the benefit of our method
lies specifically in the fact that a temperature range is given as an input.
Achieving the same result as the SAD method with 1/t-WL would either require
multiple simulations over a wider range of energies, or would require guessing
in advance a wider range of energies than are needed.  In either case, the
convergence of 1/t-WL would be worse than our tests indicate. We have modified
the conclusion to better emphasize this important distinction.

**----------------------------------------------------------------------------**

1. The referee does not acknowledge that our method is based on SAMC (the
mathematical generalization of WL). In fact, the referee does not seem to
acknowledge *the existence of the SAMC method* which we find curious. The
referee states that "the original WL paper does not specify a scheme for
updating the update factor."  This is false.  Both of the 2001 WL papers specify
the same scheme that is generally used in when the WL method is used (gamma
drops by a factor of 2).  It is true that the papers do not *mandate* this
schedule.  However, neither our method nor SAMC can be considered an
implementation of the WL method, because the WL method *does* mandate that the
update factor is only decreased when the histogram has become sufficiently flat.

Our method clearly does *not* implement a new update scheme for the WL method.
We also do not simply implement a new update scheme for SAMC, since SAMC
specifies an update schedule which is predetermined.  As stated in Section I
*'In this work, we have developed an improved algorithm based on SAMC.'*  This
idea is again reinforced in Section III.
